---
title: "R Notebook"
output: html_notebook
editor_options: 
  chunk_output_type: console
---
```{r env}
library(tidyverse)
library(dtplyr)
```


```{r get-data}
library(DBI)
library(RPostgres)
library(getPass)

host <- "127.0.0.1"
port <- 5432
db <- 'gradschool'
usr <- 'postgres'


conn <- DBI::dbConnect(RPostgres::Postgres(), user=usr, password=getPass::getPass(), dbname=db)
stopifnot(DBI::dbIsValid(conn))


dfs <- list()
for(metro in c('chi','phi','nyc','sfba')) {
  print(paste0(metro, '..'))
  dfs[[metro]] <- tbl(conn, DBI::Id('cyp204d_final_project', paste0(metro, '_final_datasets'))) %>%
    as_tibble() %>%
    collect()
}
```

```{r}
setwd('~/Documents/Grad School/Berkeley/Classes/CYP_204D - Multivariate Analysis in Planning/final_project_redo/code')
df_phi <- read_csv('data/exports/phi_zones_raw_trips.csv') %>% select(-`...1`)

```


## Clean Data
```{r}
modes <- c('auto_passenger', 'biking', 'commercial', 'on_demand_auto','other_travel_mode', 'private_auto', 'public_transit', 'walking')

for(metro in c('chi','phi','nyc','sfba')) {
  dfs[[metro]] <- 
    dfs[[metro]] %>% 
    mutate(
      active_share = (walking + biking)/(auto_passenger + on_demand_auto + private_auto + walking + biking + public_transit),
      car_share = (auto_passenger + on_demand_auto + private_auto)/(walking + biking + auto_passenger + on_demand_auto + private_auto + public_transit)
    )
}

df_combined <- dfs %>% bind_rows(.id = 'metro')

```

## Gather More Data

### Get Census data
```{r}
# census2020_vars <- tidycensus::load_variables(2020, 'dhc', TRUE)
# census2020_vars %>% separate(col = 'label', into = paste0('col', seq(1,10)), sep = '!!') %>% distinct(col3) %>% View()
# tidycensus::load_variables(2020, 'dp', TRUE) %>% separate(col = 'label', into = paste0('col', seq(1,10)), sep = '!!') %>% distinct(col3) %>% View()
# 
# # Full acs5
# median_income_cols <- 
#   tidycensus::load_variables(2022, 'acs5', TRUE) %>% 
#   separate(col = 'label', into = paste0('col', seq(1,10)), sep = '!!') %>%
#   filter(str_detect(col2, 'income'), col3 == 'Total:', is.na(col4)) %>%
#   select(name, col2)
# 
# # Pull income cols from ACS at BG level for CA
# CA_acs_income_cols <- tidycensus::get_acs(variables = median_income_cols$name, year = 2022, geography = 'block group', state = 'CA')
# 
# # figure out which ones aren't null at block group level
# CA_acs_income_cols %>%  
#   filter(!is.na(estimate)) %>% # 47.9k
#   distinct(variable, .keep_all = TRUE) # only B19049_001, B25092_001
# 
# # Let's check what those are
# median_income_cols %>%
#   filter(name %in% c('B19049_001', 'B25092_001')) # ok, B19049_001 is my guy, B25092_001 is owner housing costs 

```

### Get all for each state
```{r}
# Create summary of each county
STATES.counties <-
  df_combined %>%
  mutate(fips5 = substr(fips12_o, 1, 5)) %>%
  group_by(metro, fips5) %>%
  summarize(n_BGs = n_distinct(fips12_o)) %>%
  mutate(fips2 = substr(fips5, 1,2)) %>%
  inner_join(
    tidycensus::fips_codes %>% 
      distinct(state, state_code),
    by = c('fips2' = 'state_code')
  )
  
# Loop to get acs vars
# dfs.med_inc <- list()
# for(m in unique(STATES.counties$metro)) {
#   cat(paste0(m, '..'))
#   # filter to dict
#   metro_counties <- 
#     STATES.counties %>%
#     filter(metro == m)
#   
#   dfs.med_inc[[m]] <- 
#     tidycensus::get_acs(variables = 'B19049_001', year = 2023, geography = 'block group', state = unique(metro_counties$state)) %>%
#     mutate(fips5 = substr(GEOID, 1,5)) %>%
#     inner_join(
#       metro_counties,
#       by = c('fips5' = 'fips5')
#     )
# }
# 
# # Combine
# df.med_inc <- 
#   dfs.med_inc %>% 
#   bind_rows(.id = 'metro')
# 
# # Med Inc
# df.med_inc %>% 
#   ggplot(aes(x = estimate)) + 
#   geom_histogram(bins = 50) + 
#   facet_wrap(~metro) # weird the huge spike at 250k, but I guess that's the maximum?
# 
# ```
# 
# ### Join in to census
# ```{r}
# mean(str_length(df.med_inc$GEOID) == 12) # all are 12
# df_combined <- 
#   df_combined %>%
#   inner_join(
#     df.med_inc %>%
#       select(GEOID, o_medinc = estimate),
#     by = c('fips12_o'='GEOID')
#   ) %>%
#   inner_join(
#     df.med_inc %>%
#       select(GEOID, d_medinc = estimate),
#     by = c('fips12_d'='GEOID')
#   ) 
# 
# # 
```


### Scales
```{r}
# df_combined$d_medinc_Z <- scale(df_combined$d_medinc)[,1]
# df_combined$o_medinc_Z <- scale(df_combined$o_medinc)[,1]

```


## Redo for Car ownership rates
```{r}
# car_ownership_cols <- 
#   tidycensus::load_variables(2023, 'acs5', TRUE) %>% 
#   separate(col = 'label', into = paste0('col', seq(1,10)), sep = '!!') %>%
#   filter(str_detect(col3, 'vehicle'), col2 == 'Total:', is.na(col4)) %>%
#   select(name, col2)
# 
# car_ownership_cols[str_detect(car_ownership_cols$label, 'vehicle'), ]
# 
# # Results
# # 'B25046_001' Aggregate Number of Vehicles available - so only this 
# # 'B08015_001' Aggregate Number of Vehicles used in commuting
# 
# # Check geo-level
# temp <- tidycensus::get_acs(variables = c('B25046_001','B08015_001'), year = 2023, geography = 'block group', state = unique(metro_counties$state))
# temp %>% 
#   group_by(variable) %>%
#   summarize(
#     n(), sum(!is.na(estimate))
#   )  # - so only B25046_001 works at BG level
# 
# # Let's try Tract
# temp <- tidycensus::get_acs(variables = c('B25046_001','B08015_001'), year = 2023, geography = 'tract', state = unique(metro_counties$state))
# # ok so B08015_001 is at the tract level
# 
# 
# dfs.car_ownership <- list()
# 
# for(m in unique(STATES.counties$metro)) {
#   cat(paste0(m, '..'))
#   # filter to dict
#   metro_counties <- 
#     STATES.counties %>%
#     filter(metro == m)
#   
#   dfs.med_inc[[m]] <- 
#     tidycensus::get_acs(variables = 'B19049_001', year = 2023, geography = 'block group', state = unique(metro_counties$state)) %>%
#     mutate(fips5 = substr(GEOID, 1,5)) %>%
#     inner_join(
#       metro_counties,
#       by = c('fips5' = 'fips5')
#     )
# }
```

# Actual Census run
```{r act}
# Gather census vars:
# - Identify vars

census_vars <- c('total_pop' = 'B01003_001', 'n_veh_available' = 'B25046_001', 'n_veh_commute' = 'B08015_001', 'medinc' = 'B19049_001')
dfs.census <- list()
for(m in unique(STATES.counties$metro)) {
  cat(paste0(m, '..'))
  # filter to dict
  metro_counties <- 
    STATES.counties %>%
    filter(metro == m)
  
  # - get at Block group level
  df.census.bg <- tidycensus::get_acs(variables = census_vars, year = 2023, geography = 'block group', state=unique(metro_counties$state)) %>% 
    pivot_wider(id_cols = 'GEOID', names_from = 'variable', values_from = 'estimate') %>% 
    mutate(veh_pp = n_veh_available/total_pop, veh_commute_pp = n_veh_commute/total_pop) %>%
    select(-c(n_veh_commute, n_veh_available))
  
  # - get at tract level
  df.census.tract <- tidycensus::get_acs(variables = census_vars, year = 2023, geography = 'tract', state=unique(metro_counties$state)) %>%
    pivot_wider(id_cols = 'GEOID', names_from = 'variable', values_from = 'estimate') %>% 
    mutate(veh_pp = n_veh_available/total_pop, veh_commute_pp = n_veh_commute/total_pop) %>%
    select(-c(n_veh_commute, n_veh_available))
  # - get at county level
  df.census.cty <- 
    tidycensus::get_acs(variables = census_vars, year = 2023, geography = 'county', state=unique(metro_counties$state)) %>%
    pivot_wider(id_cols = 'GEOID', names_from = 'variable', values_from = 'estimate') %>% 
    mutate(veh_pp = n_veh_available/total_pop, veh_commute_pp = n_veh_commute/total_pop) %>%
    select(-c(n_veh_commute, n_veh_available))
  # - fill in block group level with census tract level where necessary
  
  dfs.census[[m]] <- 
    df.census.bg %>% 
    rename(fips12 = GEOID) %>%
    mutate(
      fips11 = substr(fips12,1,11),
      fips5 = substr(fips12,1,5)
    ) %>%
    left_join(
      df.census.tract,
      by = c('fips11'='GEOID'),
      suffix = c('','.tract')
    ) %>%
    left_join(
      df.census.cty,
      by = c('fips5'='GEOID'),
      suffix = c('','.cty')
    ) %>%
    mutate(
      total_pop = coalesce(total_pop, total_pop.tract, total_pop.cty),
      level_medinc = if_else(!is.na(medinc), 'bg', if_else(!is.na(medinc.tract), 'tract', if_else(!is.na(medinc.cty), 'cty', 'other'))),
      level_veh_pp = if_else(!is.na(veh_pp), 'bg', if_else(!is.na(veh_pp.tract), 'tract', if_else(!is.na(veh_pp.cty), 'cty', 'other'))),
      level_veh_commute_pp = if_else(!is.na(veh_commute_pp), 'bg', if_else(!is.na(veh_commute_pp.tract), 'tract', if_else(!is.na(veh_commute_pp.cty), 'cty', 'other'))),
      medinc = coalesce(medinc, medinc.tract, medinc.cty),
      veh_pp = coalesce(veh_pp, veh_pp.tract, veh_pp.cty),
      veh_commute_pp = coalesce(veh_commute_pp, veh_commute_pp.tract, veh_commute_pp.cty)
    ) %>%
    select(
      fips12, fips5, total_pop, medinc, veh_pp, veh_commute_pp, level_medinc, level_veh_pp, level_veh_commute_pp
    )
}

dfs.census %>% 
  bind_rows(.id='metro') %>%
  group_by(across(starts_with('level_'))) %>%
  summarize(n=n()) %>%
  arrange(desc(n))

# TODO: it is taking some variables at the tract or county level and then dividing by the population at the blockgroup level
# We need to do the estimates before 
```

### Normalize
```{r}
df_census <- 
  dfs.census %>%
  bind_rows(.id='metro') %>%
  fastDummies::dummy_cols(c('level_medinc', 'level_veh_pp', 'level_veh_commute_pp')) %>%
  mutate(medinc_Z = as.numeric(scale(medinc)))
  

df_census %>%
  write_csv('../data/exports/bg2census.csv')
```

## Model



# By BG Dataset
```{r}
df_modeling <- 
  df_combined %>%
  mutate(
    dist_1km = dist/1000,
    extra_zonal = if_else(zone_same, 0, 1),
    active_share_ = coalesce(active_share,0)/(coalesce(active_share,0) + coalesce(car_share, 0)),
    total_active = coalesce(active_share,0) * total_trips,
    extra_county = if_else(substr(fips12_o, 1, 5) != substr(fips12_d, 1, 5), 1, 0),
    metro_label = case_when(
      metro == 'nyc' ~ 'New York',
      metro == 'chi' ~ 'Chicago',
      metro == 'phi' ~ 'Philadelphia',
      metro == 'sfba' ~ 'SF Bay Area'
    )
  ) %>%
  inner_join(
    df_census %>%
      rename_all(~paste0(.x, '_o')),
    by = c('fips12_o'='fips12_o')
  ) %>%
  inner_join(
    df_census %>%
      rename_all(~paste0(.x, '_d')),
    by = c('fips12_d'='fips12_d')
  )
  
```

### Basic tests
```{r}
bivariate_model <- lm(active_share ~ extra_zonal, data=df_modeling)
bivariate_model.wtd <- glm(active_share ~ extra_zonal, data=df_modeling, weights = total_trips, family='binomial')
summary(bivariate_model)
summary(bivariate_model.wtd)

library(stargazer)
stargazer::stargazer(bivariate_model.wtd, type = 'html')


# T Test
t.test(
  df_modeling %>% filter(extra_zonal == 1) %>% pull('active_share'),
  df_modeling %>% filter(extra_zonal == 0) %>% pull('active_share'),
  var.equal = TRUE
)

mean(df_modeling %>% filter(extra_zonal == 0) %>% pull('active_share'), na.rm=T)

df_modeling %>% 
  #group_by(metro, metro_label, extra_zonal) %>%
  filter(dist_1km != 0) %>%
  group_by(extra_zonal) %>%
  summarize(
    n = n(),
    avg = mean(active_share, na.rm=T),
    wtd_avg = sum(active_share * total_trips, na.rm=T)/sum(total_trips, na.rm=T)
  )# %>%
  ggplot(aes(x = if_else(extra_zonal == 1, 'Extra-Zonal', 'Intra-Zonal'), fill=metro, y = wtd_avg)) + 
  geom_bar(stat='identity') + 
  geom_label(aes(label=scales::percent(wtd_avg)), fill='#efefef') + 
  scale_fill_manual(values=METRO_COLORS, guide=FALSE) + 
  scale_y_continuous(labels=scales::percent_format()) +
  labs(
    x = 'Trip Type',
    y = 'Share Active Transport (Weighted)'
  ) + 
  facet_wrap(~metro_label)
  pull()

```

### Basic test model
```{r investigate-data}

nrow(df_combined) # 1.66M
nrow(df_modeling) # 1.66M
df_modeling$zone_same
#test_model <- lm(active_share ~ zone_same, data=dfs %>% bind_rows())
test_model <- lm(active_share ~ extra_zonal + dist_1km + metro, data=df_modeling)
summary(test_model)
coef(test_model)






```

### Add in income
```{r add-in-income}
income_model <- lm(active_share ~ extra_zonal + dist_1km + metro + medinc_Z_d + medinc_Z_o, data=df_modeling)
summary(income_model)
coef(income_model)
car::vif(income_model)

# ok so, including income, its about the same as an additional 180m
```

so NYC is a huge outlier bc of public transit to cross rivers

### remove Public Transit
```{r}
income_model.no_transit <- lm(active_share_ ~ extra_zonal + dist_1km + metro + medinc_Z_d + medinc_Z_o, data=df_modeling)
summary(income_model.no_transit) # ok so not that different. Still think the river thing is a problem

# We can isolate this by including a "different_county" var
```

### Include extra-county
```{r}
income_model.no_transit.extra_county <- lm(
  active_share_ ~ extra_zonal + dist_1km + metro + medinc_Z_d + medinc_Z_o + extra_county, 
  data=df_modeling
)

summary(income_model.no_transit.extra_county)
#car::vif(income_model.no_transit.extra_county)
## Interesting, surprisingly doesn't make that much of a difference
```

```{r}
model.extra_county.ny_only <- lm(
  active_share_ ~ extra_zonal + dist_1km + medinc_Z_d + medinc_Z_o + extra_county, 
  data=df_modeling %>%
    filter(metro == 'nyc')
)
summary(model.extra_county.ny_only) # so leaving your burrough is close to like 680km and 4 times as powerful as leaving your zone alone.
# Need a distance to transit, or something about transit because in Chicago this may just be saying people are more likely to use active transit, the further they are from an L stop?
```



### Split by Metro
```{r split-by-metro}
# sfba
income_model.sfba <- lm(active_share_ ~ extra_zonal + dist_1km + medinc_Z_d + medinc_Z_o, data=df_modeling %>% filter(metro=='sfba'))
summary(income_model.sfba)
coef(income_model.sfba) 
# leaving zone is about the same as 400 meters

# Chicago
income_model.chi <- lm(active_share ~ extra_zonal + dist_1km + medinc_Z_d + medinc_Z_o, data=df_modeling %>% filter(metro=='chi'))
summary(income_model.chi)
coef(income_model.chi)

# So NYC is a problem, because we need to remove public transit
```

### Multinomial Logit
```{r multinomial-logit}
model.binom <- glm(
  active_share ~ extra_zonal + dist_1km + d_medinc_Z + o_medinc_Z + extra_county + metro,
  family = 'binomial',
  data = df_modeling
)

summary(model.binom)
```

### Multinomial Logit - totals
```{r multinomial-logit}
df_modeling

model.binom <- glm(
  active_share ~ extra_zonal + dist_1km + d_medinc_Z + metro + o_medinc_Z + extra_county,# + metro,
  weights = total_trips,
  family = 'binomial',
  data = df_modeling %>% filter(fips12_d != fips12_o)#, metro == 'nyc')
)

summary(model.binom) # about half a km effect in NYC, but elsewhere it is positive!
# I think something that is happening is that density is having a major effect here and car ownership
```

## Redo Modeling with more census Data
```{r}
model10 <- glm(
  #active_share_ ~ extra_zonal + dist_1km + extra_county + medinc_Z_o + medinc_Z_d + veh_pp_o + veh_commute_pp_o, 
  active_share ~ extra_zonal + dist_1km + medinc_Z_o + medinc_Z_d + metro +  total_trips + public_transit,
  weights = total_trips,
  family = 'binomial',
  data=df_modeling %>%
    filter(
      fips12_d != fips12_o#,
      #metro=='nyc'
    )
)

summary(model10)
car::vif(model10)

df_modeling %>%
  mutate(self_trip = if_else(dist==0, 'self-trip', 'no-self')) %>%
  #group_by(self_trip, extra_county, extra_zonal, zone_same) %>%
  group_by(metro_label, extra_zonal) %>%
  summarize(
    n_bg_pairs=n(),
    active_share_ = sum(active_share_ * total_trips, na.rm=T)/sum(total_trips, na.rm=T),
    mean_dist = sum(dist * total_trips, na.rm=T)/sum(total_trips, na.rm=T),
    total_trips=sum(total_trips)
  ) %>%
  #ggplot(aes(x = if_else(extra_zonal==1, 'Outside of Zone', 'Intra-Zone'), y = active_share_)) + 
  ggplot(aes(x = if_else(extra_zonal==1, 'Outside of Zone', 'Intra-Zone'), y = mean_dist)) + 
  geom_bar(stat='identity') + 
  labs(
    x = 'Trip Type',
    y = 'Share of Trip Active'
  ) + 
  # scale_y_continuous(labels=scales::percent_format()) + 
  scale_y_continuous(labels=scales::number_format()) + 
  facet_wrap(~metro_label)

sum(is.na(df_modeling$total_trips))
sum(is.na(df_modeling$active_share_)) # 68457
sum(is.na(df_modeling$active_share)) # 11,215

# here says its close to 420m
#summary(lm(active_share_ ~ extra_zonal + dist_1km + extra_county + medinc_Z_o + medinc_Z_d + total_pop_o + total_pop_d + veh_pp_o + veh_pp_d + veh_commute_pp_o + veh_commute_pp_d, data=df_modeling %>% filter(metro == 'chi')))
```

## Descriptive Data

### 
```{r}
df_modeling %>%
  group_by(metro, metro_label, zoneID_o) %>%
  summarize(
    n_BGs = n_distinct(fips12_o),
    total_trips = sum(total_trips)
  ) %>%
  ggplot(aes(x=n_BGs)) + 
  geom_histogram(aes(fill=metro)) + 
  facet_wrap(~metro_label) + 
  scale_fill_manual(values=METRO_COLORS, guide=FALSE) + 
  scale_x_continuous(labels=scales::number) + 
  labs(
    y = 'Count of Distinct Zones',
    x = 'Number of Block Groups in Each Zone'
  )
```

### N zones
```{r}

n_zones <- 
  tribble(
    ~metro, ~`Total Zones`, ~`> 1km`, ~`Match to BG`,
    'chi', 1994, 54, 54,
    'phi', 291, 15, 15,
    'nyc', 1683, 79, 89,
    'sfba', 3573, 70, 63
  )
n_zones %>%
  mutate(
    metro_label = case_when(
      metro == 'nyc' ~ 'New York',
      metro == 'chi' ~ 'Chicago',
      metro == 'phi' ~ 'Philadelphia',
      metro == 'sfba' ~ 'SF Bay Area'
    )
  ) %>%
  mutate(across(is.numeric, ~ .x/`Total Zones`, .names = '{.col}__share')) %>%
  pivot_longer(cols = -c('metro','metro_label')) %>%
  separate(name, into=c('name','name2'), sep='__') %>%
  mutate(name2 = coalesce(name2, 'raw')) %>%
  pivot_wider(names_from='name2', values_from='value') %>%
  ggplot(aes(x = fct_inorder(name), fill=metro, y = share, label=paste0(scales::comma(raw), if_else(share != 1, paste0(' (',scales::percent(share, accuracy=1L), ')'), '')))) + 
  geom_bar(stat='identity') + 
  scale_fill_manual(values=METRO_COLORS, guide=FALSE) + 
  scale_y_continuous(labels=scales::percent_format()) + 
  geom_label(fill='#efefef', nudge_y = -.01) + 
  labs(
    x = NULL,
    y = NULL
  ) + 
  facet_wrap(~metro_label, scale='free_y')
```

### Trip Distance 
```{r}
df_modeling %>%
  
```

### Active Share by intra/extra-zonal
```{r active-share by intra/extra-zonal}
df_modeling %>%
  group_by(metro_label, extra_county, extra_zonal) %>%
  summarize(
    n = n(), 
    total_trips_sum = sum(total_trips), 
    active_share = weighted.mean(active_share, total_trips, na.rm = T)
  ) %>%
  mutate(
    extra_county = if_else(extra_county == 1, 'Extra-County', 'Intra-County'),
    extra_zonal = if_else(extra_zonal == 1, 'Extra-Zonal', 'Intra-Zonal'),
    combined = paste(extra_county, '~\n', extra_zonal)
  ) %>%
  ggplot(aes(x = as_factor(combined), group=as_factor(combined), y = active_share, fill=total_trips_sum)) + 
  geom_bar(stat = 'identity', position='dodge') + 
  scale_y_continuous(labels=scales::percent_format(), limits = c(0,1)) + 
  scale_fill_gradient(low = '#a0a0a0', high='dodgerblue4', labels=scales::number_format(scale=1/100000, suffix = 'M')) +
  theme(
    axis.text.x.bottom = element_text(angle = 0, vjust=.5)
  ) + 
  labs(
    fill = 'Total_trips',
    y = 'Active Share',
    x = 'Location'
  ) + 
  geom_label(aes(label=scales::percent(active_share, accuracy=.1)), fill='#efefef') + 
  facet_wrap(~metro_label)

```

## Summary Stats & Plots
```{r}
library(vtable)
df_modeling %>% 
  select(dist_1km, active_share_, extra_zonal, metro = metro_label, total_trips) %>%
  st(group='metro',group.long=TRUE, add.median = TRUE, group.weights = 'total_trips')
```

```{r}
METRO_COLORS <- RColorBrewer::brewer.pal(4, 'Pastel2')
#colorspace::hcl_
METRO_COLORS <- c('chi' = '#0E3386', 'sfba' = '#fe5a1d', 'phi' = '#004C54', 'nyc' = 'grey65')
```

### histogram trips
```{r}
df_modeling %>%
  filter(fips12_o != fips12_d) %>%
  # ggplot(aes(x = active_share_)) +
  ggplot(aes(x = active_share_, weight=total_trips)) + 
  geom_histogram(fill = 'indianred2') + 
  # Scales
  scale_x_continuous(labels=scales::percent_format()) + 
  scale_y_continuous(labels=scales::number_format(scale=1/1000, suffix='k')) + 
  scale_fill_manual(values=METRO_COLORS, guide=FALSE) + 
  # Labels
  labs(
    x = 'Active Share',
    y = 'Total Trips'
    #y = 'Block Group Pairs'
  )# +
  #facet_wrap(~metro_label, scale='free_y')
```
### histogram trips - metro

```{r}

df_modeling %>%
  filter(fips12_o != fips12_d) %>%
  ggplot(aes(x = active_share_, fill = metro)) + 
  # ggplot(aes(x = active_share_, weight=total_trips, fill=metro)) + 
  geom_histogram() + 
  # Scales
  scale_x_continuous(labels=scales::percent_format()) + 
  scale_y_continuous(labels=scales::number_format(scale=1/1000, suffix='k')) + 
  scale_fill_manual(values=METRO_COLORS, guide=FALSE) + 
  # Labels
  labs(
    x = 'Active Share',
    y = 'Block Group pairs'
  ) +
  facet_wrap(~metro_label, scale='free_y')
```


## Statistical Tests
### T-test
```{r}
install.packages('infer')
df_modeling %>%
  infer::t_test(active_share ~ extra_zonal, weight)

df_modeling %>%
  filter(metro == 'phi') %>%
  head(10) %>%
  select(fips12_o, fips12_d, total_trips, dist, active_share_, car_share) -> test
  
test %>%
  purrr::walk(
    #\(x) rep(c(x$fips12_o, x$fips12_d, 1, x$dist, x$active_share_, x$car_share), x$total_trips),
    #\(x) print(x['fips12_p']),
    function(x) print(x),
    .progress = TRUE
  )

for(i in test) {
  print(i)
}

df_modeling

#replicate(test[1,]$total_trips, test[1,], simplify='list') %>% data.frame() %>% t() %>% as_tibble()
```

```{python}
!pip install statsmodels
import statsmodels.api as sm
```